Doppler Imaging Fun

### 2019-07-03 tex/gitlinks.tex
more text

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-03 tex/ms.tex
more text

%
\section{The problem}
\label{sec:the_problem}
%
Let $I(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
intensity observed 
at log wavelength $\xi \equiv \ln\lambda$ and at sky-projected 
Cartesian position $\mathbf{x} = (x, y, z)$ on the surface of the 
star at time $t$, where
$\mathbf{d}$ is a set of arbitrary parameters of the Doppler field.
We may express this intensity as
%
\begin{align}
    \label{eq:intro:Ixi}
    I(\xi, \mathbf{x}, t, \mathbf{d}) &= 
        I_0\Big(\xi_0(\xi, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
\end{align}
%
where $I_0$ is the specific intensity at each point on the star 
in the surface rest frame and 
%
\begin{align}
    \label{eq:intro:xi0}
    \xi_0(\xi, \mathbf{x}, \mathbf{d}) &= 
    \xi + \mathcal{D}(\mathbf{x}, \mathbf{d})
\end{align}
%
is the log wavelength in the rest frame. The quantity $\mathcal{D}$ is
computed from the formula for the Doppler shift and is equal to
%
\begin{align}
    \label{eq:intro:D}
    \mathcal{D}(\mathbf{x}, \mathbf{d}) 
        &=
        \frac{1}{2}\ln\left( 
            \frac{1 - \beta(\mathbf{x}, \mathbf{d})}{1 + \beta(\mathbf{x}, 
            \mathbf{d})} 
        \right)
\end{align}
%
where $\beta = v(\mathbf{x}, \mathbf{d}) / c$ is the ratio of the 
radial velocity at a point on the surface of the star to the speed of light.
In keeping with the literature, we take positive values of $v$ to mean 
redshifts.

@@

The equation for the specific intensity now reads
%
\begin{align}
    \label{eq:solution:Ixi0vecfull}
    I_0(\xi_0, \mathbf{x}, t) &=
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathbf{R}(t)
    \bvec{a}(\xi_0)
    \quad ,
\end{align}
%
where it is clear that we have fully separated the spatial, temporal, and
spectral terms. However, in order to compute the observed spectrum, we must
still Doppler shift this expression and integrate it over the visible
portion of the star. To this end, it is convenient to express the Doppler
shift as a convolution
of the spectrum in the rest frame with a delta function:
%
\begin{align}
    I(\xi, \mathbf{x}, t) &= 
        I_0(\xi_0, \mathbf{x}, t) 
        * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
        \quad,
\end{align}
%
where $*$ denotes the convolution operation, 
returning a function of the shifted log wavelength, $\xi$.
Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
over the visible portion of the star, we arrive at the expression for the 
observed spectrum:
%
%
\begin{align}
    \label{eq:solution:Fxi}
    F(\xi, t) &=
    \iint\limits_{\mathcal{S}(\mathbf{x})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathbf{R}(t)
    \bvec{a}(\xi_0)
    * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
    \mathrm{d}\mathcal{S}(\mathbf{x})
    \nonumber \\[0.5em]
    &=
    \mathbf{g}^\top(\mathcal{D})
    *
    \,
    \mathbf{R}(t)
    \,
    \bvec{a}(\xi_0)
    \quad ,
\end{align}
%
%
where we made use of the commutativity of the convolution operator and 
the fact that the integral is taken only over the spatial dimensions.
We further define
%
\begin{align}
    \label{eq:solution:g}
    \mathbf{g}^\top(\mathcal{D})
    &\equiv
    \iint\limits_{\mathcal{S}(\mathbf{x})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
    \mathrm{d}\mathcal{S}(\mathbf{x})
    \nonumber \\[0.5em]
    &=  
    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
    \quad.
\end{align}
%
where the integral in the second line denotes the line integral about
some function $\mathcal{C}(\mathbf{x}, \mathbf{d})$ corresponding to the
set of all points on the visible disk where 
$\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$.

Equation~(\ref{eq:solution:Fxi}) is the complete deconvolution of the
observed spectrum into velocity terms, temporal terms, and spectral/spatial
terms, respectively. In the following sections, we will discuss how to
efficiently solve Equation~(\ref{eq:solution:g}).

\section{Doppler imaging of rigid rotators}
\label{sec:rigid}
%
In the case that the star's rotation is rigid (i.e., differential rotation
is negligible) and other effects such as convective blueshift
may be ignored, the radial velocity at any point on the surface is 
simply proportional to the distance to the axis of rotation. Without loss
of generality, if we assume the axis of rotation lies along the $y-z$ plane,
we have
%
\begin{align}
    \beta(\mathbf{x}, \mathbf{d}) = \frac{\omega \sin i \, x}{c}
\end{align}
%
and
%
\begin{align}
    \label{eq:rigid:D}
    \mathcal{D}(\mathbf{x}, \mathbf{d}) &= 
        \frac{1}{2}\ln\left( 
            \dfrac{1 - \dfrac{\omega \sin i \, x}{c}}
                 {1 + \dfrac{\omega \sin i \, x}{c}}
        \right)
    \quad ,
\end{align}
%
where the parameters $\mathbf{d}$ of the Doppler field are the
angular velocity, $\omega$, and the inclination of the star with
respect to $\hat{y}$, $i$.

In order to solve Equation~(\ref{eq:solution:g}), let us change basis from
spherical harmonics to polynomials on the sphere:
%
\begin{align}
    \label{eq:rigid:g}
    \mathbf{g}^\top(\mathcal{D}) &\equiv
    \bvec{s}^\top(\mathcal{D})
    \bvec{A_1}
\end{align}
%
where
%
\begin{align}
    \label{eq:rigid:sTdef}
    \mathbf{s}^\top(\mathcal{D})
    &\equiv
    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
    \tilde{\bvec{p}}^\top(\mathbf{x})
    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
\end{align}
%
is the vector of integral solutions for each spherical harmonic,
%
\begin{align}
    \tilde{\bvec{p}}(\mathbf{x}) \equiv 
\Big( 
    1 \quad\quad\quad\quad\quad\quad 
    x \quad\quad\quad\quad\quad\quad 
    z \quad\quad\quad\quad\quad\quad 
    y \quad\quad\quad\quad\quad\quad 
    x^2 \quad\quad\quad\quad\quad\quad 
    xz \quad\quad\quad\quad\quad\quad 
    xy \quad\quad\quad\quad\quad\quad
    yz \quad\quad\quad\quad\quad\quad 
    y^2 \quad\quad\quad\quad\quad\quad
    ... 
\Big)^\top
\end{align}
%
is the polynomial basis \citep[Equation 7 in][]{Luger2019},
and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
to polynomials 
\citep[Equation B11 in][]{Luger2019}. On the observer-facing surface of 
the unit sphere, the coordinate $z$ is given by $\sqrt{1 - x^2 - y^2}$.

If
we assume the star is unocculted, the region of integration $\mathcal{S}$ 
is simply the unit disk, so $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
is the set of all points
that satisfy both $\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$ and 
$x^2 + y^2 \le 1$.
Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
the curves $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
are simply vertical lines on the unit disk given by
%
\begin{align}
    x(\mathcal{D}) &= 
        \Bigg(\frac{c}{\omega\sin i}\Bigg) 
        \Bigg(\frac{1 - \mathrm{e}^{2\mathcal{D}}}
                   {1 + \mathrm{e}^{2\mathcal{D}}}\Bigg)
    \quad .
\end{align}
%
The integral in Equation~(\ref{eq:rigid:sTdef}) is therefore just an integral
over $y$:
%
\begin{align}
    \label{eq:rigid:sT}
    \bvec{s}^\top(\mathcal{D}) 
    &=    
    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
                {\sqrt{1 - x(\mathcal{D})^2}}
    \tilde{\bvec{p}}^\top
    \Big(x(\mathcal{D}), y\Big)
    \mathrm{d}y
    \quad .
\end{align}
%
From \citet{Luger2019}, the $n^\mathrm{th}$ term of the polynomial basis
is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
%
\begin{proof}{PolynomialBasis}
    \tilde{p}_n 
    &=
    x^i y^j z^k
\end{proof}
%
where $i, j, k$ are integers given by
%
\begin{proof}{PolynomialBasis}
    \label{eq:lm}
    i &= \floor*{\Lambda - \Delta}
    \nonumber \\[0.5em]
    j &= \floor*{\Delta}
    \nonumber \\[0.5em]
    k &= \ceil*{\Delta} - \floor*{\Delta}
\end{proof}
%
with
%
\begin{proof}{PolynomialBasis}
    \Lambda &= \floor*{\sqrt{n}}
    \nonumber \\[0.5em]
    \Delta &= \frac{n - \Lambda^2}{2}
    \quad .
\end{proof}
%
We may now explicitly write down the $n^\mathrm{th}$ term of 
Equation~(\ref{eq:rigid:sT}),
%
\begin{align}
    s_n(\mathcal{D}) 
    &=    
    x(\mathcal{D})^i
    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
                {\sqrt{1 - x(\mathcal{D})^2}}
        y^j
        \left(1 - x(\mathcal{D})^2 - y^2\right)^{\frac{k}{2}} \,
    \mathrm{d}y 
    \quad ,
\end{align}
%
and solve it analytically:
%
\begin{align}
        \label{eq:rigid:sTAnalytic}
        s_n(\mathcal{D}) 
        &=     
    \begin{dcases}
        0
        &
        \qquad j \, \mathrm{odd}
        \\[1em]
        \frac{2 x(\mathcal{D})^i 
        \big(1 - x(\mathcal{D})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
        &
        \qquad k = 0
        \\[1em]
        x(\mathcal{D})^{i} \mathcal{I}_{j}
        \big(x(\mathcal{D})\big)
        &
        \qquad k = 1
        \quad ,
    \end{dcases}
\end{align}
%
where $\mathcal{I}_j(x)$ is computed analytically
from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
with $\mathcal{I}_0(x)$ given by Equation~(\ref{eq:app:I0}).

\appendix

\section{Integrals}
\subsection{Equation~(\ref{eq:rigid:sTAnalytic})}
%
When $k = 1$, we may write the $n^\mathrm{th}$ component
of Equation~(\ref{eq:rigid:sTAnalytic}) as
%
\begin{align}
    s_n(\mathcal{D}) = 
        x(\mathcal{D})^{i}
        \mathcal{I}_{j}\big(x(\mathcal{D})\big)
\end{align}
%
where
%
\begin{align}
    \mathcal{I}_j(x) &\equiv
    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
        y^{j}
        \sqrt{1 - x^2 - y^2} \,
    \mathrm{d}y
    \quad.
\end{align}
%
Substituting $y = \sin\psi\sqrt{1 - x^2}$, we have
%
\begin{align}
    \mathcal{I}_j(x) &=
    %
    (1 - x^2)^{\frac{j + 2}{2}}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
        \sin^j\psi
        \cos^2\psi \,
    \mathrm{d}\psi
    \quad.
\end{align}
%
We may solve this integral using the recurrence relation
%
\begin{align}
    \int
        \sin^j\psi
        \cos^m\psi \,
    \mathrm{d}\psi
    &=
    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
    +
    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
    \quad ,
\end{align}
%
which, in our case, simplifies to
%
\begin{align}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
        \sin^j\psi
        \cos^2\psi \,
    \mathrm{d}\psi
    &=
    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
    \quad.
\end{align}
%
We thus arrive at the recurrence relation
%
\begin{align}
    \label{eq:app:Ij}
    \mathcal{I}_j(x) &=
    \frac{j - 1}{j + 2}
    (1 - x^2)
    \mathcal{I}_{j-2}(x)
    \quad.
\end{align}
%
Since this expression is only used when $j$ is even, we only need one
initial condition for upward recursion:
%
\begin{align}
    \label{eq:app:I0}
    \mathcal{I}_0(x) &\equiv
    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
        \sqrt{1 - x^2 - y^2} \,
    \mathrm{d}y
    \nonumber \\
    &= \frac{\pi}{2}(1 - x^2)
    \quad.
\end{align}

>>>>

%
\section{The problem}
\label{sec:the_problem}
%
Let $I(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
intensity observed 
at log wavelength $\xi \equiv \ln\lambda$ and at sky-projected 
Cartesian position $\mathbf{x} = (x, y, z)$ on the surface of the 
star at time $t$, where
$\mathbf{d}$ is a set of arbitrary parameters of the Doppler field.
We may express this intensity as
%
\begin{align}
    \label{eq:intro:Ixi}
    I(\xi, \mathbf{x}, t, \mathbf{d}) &= 
        I_0\Big(\xi_0(\xi, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
\end{align}
%
where $I_0$ is the specific intensity at each point on the star 
in the surface rest frame and 
%
\begin{align}
    \label{eq:intro:xi0}
    \xi_0(\xi, \mathbf{x}, \mathbf{d}) &= 
    \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})
\end{align}
%
is the log wavelength in the rest frame. The quantity $\mathcal{D}$ is
the Doppler shift in log wavelength space:
%
\begin{align}
    \label{eq:intro:D}
    \mathcal{D}(\mathbf{x}, \mathbf{d}) 
        &=
        \frac{1}{2}\ln\left( 
            \frac{1 + \beta(\mathbf{x}, \mathbf{d})}{1 - \beta(\mathbf{x}, 
            \mathbf{d})} 
        \right)
\end{align}
%
where $\beta = v(\mathbf{x}, \mathbf{d}) / c$ is the ratio of the 
radial velocity at a point on the surface of the star to the speed of light.
In keeping with the literature, we take positive values of $v$ (and
$\mathcal{D}$) to mean redshifts.

@@

The equation for the specific intensity now reads
%
\begin{align}
    \label{eq:solution:Ixi0vecfull}
    I_0(\xi_0, \mathbf{x}, t) &=
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathbf{R}(t)
    \bvec{a}(\xi_0)
    \quad ,
\end{align}
%
where it is clear that we have fully separated the spatial, temporal, and
spectral terms. However, in order to compute the observed spectrum, we must
still Doppler shift this expression and integrate it over the visible
portion of the star. To this end, it is convenient to express the Doppler
shift as a convolution
of the spectrum in the rest frame with a delta function:
%
\begin{align}
    I(\xi, \mathbf{x}, t) &= 
        I_0(\xi_0, \mathbf{x}, t) 
        * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
        \quad,
\end{align}
%
where $*$ denotes the convolution operation, 
returning a function of the shifted log wavelength, $\xi$.
Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
over the visible portion of the star, we arrive at the expression for the 
observed spectrum:
%
%
\begin{align}
    \label{eq:solution:Fxi}
    F(\xi, t) &=
    \iint\limits_{\mathcal{S}(\mathbf{x})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathbf{R}(t)
    \bvec{a}(\xi_0)
    * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
    \mathrm{d}\mathcal{S}(\mathbf{x})
    \nonumber \\[0.5em]
    &=
    \mathbf{g}^\top(\mathcal{D})
    *
    \,
    \mathbf{R}(t)
    \,
    \bvec{a}(\xi_0)
    \quad ,
\end{align}
%
%
where we made use of the commutativity of the convolution operator and 
the fact that the integral is taken only over the spatial dimensions.
We further define
%
\begin{align}
    \label{eq:solution:gT}
    \mathbf{g}^\top(\mathcal{D})
    &\equiv
    \iint\limits_{\mathcal{S}(\mathbf{x})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
    \mathrm{d}\mathcal{S}(\mathbf{x})
    \nonumber \\[0.5em]
    &=  
    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
    \tilde{\bvec{y}}^\top(\mathbf{x})
    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
    \quad.
\end{align}
%
where the integral in the second line denotes the line integral about
some function $\mathcal{C}(\mathbf{x}, \mathbf{d})$ corresponding to the
set of all points on the visible disk where 
$\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$.

Equation~(\ref{eq:solution:Fxi}) is the complete deconvolution of the
observed spectrum into velocity terms, temporal terms, and spectral/spatial
terms, respectively. In the following sections, we will discuss how to
efficiently solve Equation~(\ref{eq:solution:gT}).

\section{Doppler imaging of rigid rotators}
\label{sec:rigid}
%
In the case that the star's rotation is rigid (i.e., differential rotation
is negligible) and other effects such as convective blueshift
may be ignored, the radial velocity at any point on the surface is 
simply proportional to the distance to the axis of rotation. Without loss
of generality, if we assume the axis of rotation lies along the $y-z$ plane,
we have
%
\begin{align}
    \beta(\mathbf{x}, \mathbf{d}) = \frac{\omega \sin i \, x}{c}
\end{align}
%
and
%
\begin{align}
    \label{eq:rigid:D}
    \mathcal{D}(\mathbf{x}, \mathbf{d}) &= 
        \frac{1}{2}\ln\left( 
            \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
                 {1 - \dfrac{\omega \sin i \, x}{c}}
        \right)
    \quad ,
\end{align}
%
where the parameters $\mathbf{d}$ of the Doppler field are the
angular velocity, $\omega$, and the inclination of the star with
respect to $\hat{y}$, $i$.

In order to solve Equation~(\ref{eq:solution:gT}), let us change basis from
spherical harmonics to polynomials on the sphere:
%
\begin{align}
    \label{eq:rigid:gT}
    \mathbf{g}^\top(\mathcal{D}) &\equiv
    \bvec{s}^\top(\mathcal{D})
    \bvec{A_1}
\end{align}
%
where
%
\begin{align}
    \label{eq:rigid:sTdef}
    \mathbf{s}^\top(\mathcal{D})
    &\equiv
    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
    \tilde{\bvec{p}}^\top(\mathbf{x})
    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
\end{align}
%
is the vector of integral solutions for each spherical harmonic,
%
\begin{align}
    \tilde{\bvec{p}}(\mathbf{x}) \equiv 
\Big( 
    1 \quad\quad\quad\quad\quad\quad 
    x \quad\quad\quad\quad\quad\quad 
    z \quad\quad\quad\quad\quad\quad 
    y \quad\quad\quad\quad\quad\quad 
    x^2 \quad\quad\quad\quad\quad\quad 
    xz \quad\quad\quad\quad\quad\quad 
    xy \quad\quad\quad\quad\quad\quad
    yz \quad\quad\quad\quad\quad\quad 
    y^2 \quad\quad\quad\quad\quad\quad
    ... 
\Big)^\top
\end{align}
%
is the polynomial basis \citep[Equation 7 in][]{Luger2019},
and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
to polynomials 
\citep[Equation B11 in][]{Luger2019}. On the observer-facing surface of 
the unit sphere, the coordinate $z$ is given by $\sqrt{1 - x^2 - y^2}$.

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/g_rigid.pdf}
    \oscaption{g_rigid}{%
        The Doppler $\mathbf{g}$ basis for a rigidly rotating star
        computed from Equation~(\ref{eq:rigid:gT}) and
        Equation~(\ref{eq:rigid:sTAnalytic}) up to spherical 
        harmonic degree $l=10$. Rows correspond to the degree $l$ and
        columns correspond to the order $m$. These functions encode
        the contribution of each spherical harmonic to the rotational
        broadening of features in the stellar spectrum. Because the
        rotational axis is chosen to be aligned with $\hat{y}$,
        none of the $m < 0$ harmonics contribute
        \label{fig:g_rigid}
    }
    \end{centering}
\end{figure}

If we assume the star is unocculted, the region of integration $\mathcal{S}$ 
is simply the unit disk, so $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
is the set of all points
that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$ and 
$x^2 + y^2 \le 1$.
Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
the curves $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
are simply vertical lines on the unit disk given by
%
\begin{align}
    x(\mathcal{D}) &= 
        \Bigg(\frac{c}{\omega\sin i}\Bigg) 
        \Bigg(\frac{\mathrm{e}^{2\mathcal{D}} - 1}
                   {\mathrm{e}^{2\mathcal{D}} + 1}\Bigg)
    \quad .
\end{align}
%
The integral in Equation~(\ref{eq:rigid:sTdef}) is therefore just an integral
over $y$:
%
\begin{align}
    \label{eq:rigid:sT}
    \bvec{s}^\top(\mathcal{D}) 
    &=    
    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
                {\sqrt{1 - x(\mathcal{D})^2}}
    \tilde{\bvec{p}}^\top
    \Big(x(\mathcal{D}), y\Big)
    \mathrm{d}y
    \quad .
\end{align}
%
From \citet{Luger2019}, the $n^\mathrm{th}$ term of the polynomial basis
is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
%
\begin{proof}{PolynomialBasis}
    \tilde{p}_n 
    &=
    x^i y^j z^k
\end{proof}
%
where $i, j, k$ are integers given by
%
\begin{proof}{PolynomialBasis}
    \label{eq:lm}
    i &= \floor*{\Lambda - \Delta}
    \nonumber \\[0.5em]
    j &= \floor*{\Delta}
    \nonumber \\[0.5em]
    k &= \ceil*{\Delta} - \floor*{\Delta}
\end{proof}
%
with
%
\begin{proof}{PolynomialBasis}
    \Lambda &= \floor*{\sqrt{n}}
    \nonumber \\[0.5em]
    \Delta &= \frac{n - \Lambda^2}{2}
    \quad .
\end{proof}
%
We may now explicitly write down the $n^\mathrm{th}$ term of 
Equation~(\ref{eq:rigid:sT}),
%
\begin{align}
    s_n(\mathcal{D}) 
    &=    
    x(\mathcal{D})^i
    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
                {\sqrt{1 - x(\mathcal{D})^2}}
        y^j
        \left(1 - x(\mathcal{D})^2 - y^2\right)^{\frac{k}{2}} \,
    \mathrm{d}y 
    \quad ,
\end{align}
%
and solve it analytically:
%
\begin{align}
        \label{eq:rigid:sTAnalytic}
        s_n(\mathcal{D}) 
        &=     
    \begin{dcases}
        0
        &
        \qquad j \, \mathrm{odd}
        \\[1em]
        \frac{2 x(\mathcal{D})^i 
        \big(1 - x(\mathcal{D})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
        &
        \qquad k = 0
        \\[1em]
        x(\mathcal{D})^{i} \mathcal{I}_{j}
        \big(x(\mathcal{D})\big)
        &
        \qquad k = 1
        \quad ,
    \end{dcases}
\end{align}
%
where $\mathcal{I}_j(x)$ is computed analytically
from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
with $\mathcal{I}_0(x)$ given by Equation~(\ref{eq:app:I0}).
%
Figure~\ref{fig:g_rigid} shows the $\mathbf{g}$ basis computed from
the formulae above and Equation~(\ref{eq:rigid:gT}) up to spherical 
harmonic degree $l=10$.

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.6\linewidth]{figures/spot_rigid.pdf}
    \oscaption{spot_rigid}{%
        A caption.
        \label{fig:spot_rigid}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.65\linewidth]{figures/compare_rigid.pdf}
    \oscaption{compare_rigid}{%
        A caption.
        \label{fig:compare_rigid}
    }
    \end{centering}
\end{figure}

%
%
%
%
\appendix
%
%
%
%

\section{Integrals}
\subsection{Equation~(\ref{eq:rigid:sTAnalytic})}
%
When $k = 1$, we may write the $n^\mathrm{th}$ component
of Equation~(\ref{eq:rigid:sTAnalytic}) as
%
\begin{align}
    s_n(\mathcal{D}) = 
        x(\mathcal{D})^{i}
        \mathcal{I}_{j}\big(x(\mathcal{D})\big)
\end{align}
%
where
%
\begin{align}
    \mathcal{I}_j(x) &\equiv
    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
        y^{j}
        \sqrt{1 - x^2 - y^2} \,
    \mathrm{d}y
    \quad.
\end{align}
%
Substituting $y = \sin\psi\sqrt{1 - x^2}$, we have
%
\begin{align}
    \mathcal{I}_j(x) &=
    %
    (1 - x^2)^{\frac{j + 2}{2}}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
        \sin^j\psi
        \cos^2\psi \,
    \mathrm{d}\psi
    \quad.
\end{align}
%
We may solve this integral using the recurrence relation
%
\begin{align}
    \int
        \sin^j\psi
        \cos^m\psi \,
    \mathrm{d}\psi
    &=
    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
    +
    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
    \quad ,
\end{align}
%
which, in our case, simplifies to
%
\begin{align}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
        \sin^j\psi
        \cos^2\psi \,
    \mathrm{d}\psi
    &=
    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^
        {\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
    \quad.
\end{align}
%
We thus arrive at the recurrence relation
%
\begin{align}
    \label{eq:app:Ij}
    \mathcal{I}_j(x) &=
    \frac{j - 1}{j + 2}
    (1 - x^2)
    \mathcal{I}_{j-2}(x)
    \quad.
\end{align}
%
Since this expression is only used when $j$ is even, we only need one
initial condition for upward recursion:
%
\begin{align}
    \label{eq:app:I0}
    \mathcal{I}_0(x) &\equiv
    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
        \sqrt{1 - x^2 - y^2} \,
    \mathrm{d}y
    \nonumber \\
    &= \frac{\pi}{2}(1 - x^2)
    \quad.
\end{align}
